Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-13 ms/manuscript.Rmd
Move themes to functions

```{r plot-prep}
# Change cluster to factor
ses_div_ferns_spatial <- ses_div_ferns_spatial %>%
  mutate(taxonomic_cluster = as.factor(taxonomic_cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  mutate(phylo_cluster = as.factor(phylo_cluster) %>% fct_infreq %>% as.numeric %>% as.factor)

map_theme <- theme(
    panel.grid.major = element_line(color = "grey95", size = 0.1),
    panel.background = element_rect(fill = "grey60"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

map_theme_light <- theme(
    panel.grid.major = element_line(color = "white", size = 0.1),
    panel.background = element_rect(fill = "grey90"),
    axis.ticks = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.7)
  )

>>>>

```{r plot-prep}
# Change cluster to factor
ses_div_ferns_spatial <- ses_div_ferns_spatial %>%
  mutate(taxonomic_cluster = as.factor(taxonomic_cluster) %>% fct_infreq %>% as.numeric %>% as.factor) %>%
  mutate(phylo_cluster = as.factor(phylo_cluster) %>% fct_infreq %>% as.numeric %>% as.factor)
```
